Geoms in Animint
========================================================
```{r setup,echo=FALSE}
opts_chunk$set(fig.width=6, fig.height=4,cache=TRUE)
```

```{r setup2, warning=FALSE, message=FALSE}
library(ggplot2)
library(plyr)
library(animint)
```
### geom\_abline
```{r abline}
xydata <- data.frame(x=sort(runif(50, 0, 10)))
xydata$y <- 3+2*xydata$x + rnorm(50, 0, 1)
g1 <- ggplot() + geom_point(data=xydata, aes(x=x, y=y)) + 
  geom_abline(data=data.frame(intercept=c(3, 0), slope=c(2,1)), aes(intercept=intercept, slope=slope)) +
  ggtitle("geom_abline")
g1
gg2animint(list(g1=g1), out.dir="geoms/abline")
```
[Animint plot](geoms/abline/index.html)

### geom\_ribbon
```{r ribbon}
ribbondata <- data.frame(x=seq(0, 1, .1), ymin=runif(11, 0, 1), ymax=runif(11, 1, 2))
ribbondata <- rbind(cbind(ribbondata, group="low"), cbind(ribbondata, group="high"))
ribbondata[12:22,2:3] <- ribbondata[12:22,2:3]+1
g2 <- ggplot() + 
  geom_ribbon(data=ribbondata, aes(x=x, ymin=ymin, ymax=ymax, group=group, fill=group), alpha=.5) + 
  ggtitle("geom_ribbon")
g2
gg2animint(list(g2=g2), out.dir="geoms/ribbon")
```
[Animint plot](geoms/ribbon/index.html)

### geom\_tile
```{r tile}
tiledata <- data.frame(x=rnorm(1000, 0, 3))
tiledata$y <- rnorm(1000, tiledata$x, 3)
tiledata$rx <- round(tiledata$x)
tiledata$ry <- round(tiledata$y)
tiledata <- ddply(tiledata, .(rx,ry), summarise, n=length(rx))

g3 <- ggplot() + geom_tile(data=tiledata, aes(x=rx, y=ry, fill=n)) +
  scale_fill_gradient(low="#56B1F7", high="#132B43") + 
  xlab("x") + ylab("y") + ggtitle("geom_tile")
g3
gg2animint(list(g3=g3), out.dir="geoms/tile")
```
[Animint plot](geoms/tile/index.html)

### geom\_path
```{r path}
pathdata <- data.frame(x=rnorm(30, 0, .5), y=rnorm(30, 0, .5), z=1:30)
g4 <- ggplot() + geom_path(data=pathdata, aes(x=x, y=y), alpha=.5) +
  geom_text(data=pathdata, aes(x=x, y=y, label=z)) + 
  ggtitle("geom_path")
g4
gg2animint(list(g4=g4), out.dir="geoms/path")
```
[Animint plot](geoms/path/index.html)

### geom\_polygon
```{r polygons}
polydata <- rbind(
  data.frame(x=c(0, .5, 1, .5, 0), y=c(0, 0, 1, 1, 0), group="parallelogram", fill="blue", xc=.5, yc=.5),
  data.frame(x=c(.5, .75, 1, .5), y=c(.5, 0, .5, .5), group="triangle", fill="red", xc=.75, yc=.33)
  )
g5 <- ggplot() + 
  geom_polygon(data=polydata, aes(x=x, y=y, group=group, fill=fill, colour=fill), alpha=.5)+
  scale_colour_identity() + scale_fill_identity()+
  geom_text(data=polydata, aes(x=xc, y=yc, label=group)) +
  ggtitle("geom_polygon")
g5
gg2animint(list(g5=g5), out.dir="geoms/polygon")
```
[Animint plot](geoms/polygon/index.html)

### geom\_linerange
```{r linerange}
boxplotdata <- rbind(data.frame(x=1:50, y=sort(rnorm(50, 3, 1)), group="N(3,1)"),
                     data.frame(x=1:50, y=sort(rnorm(50, 0, 1)), group="N(0,1)"), 
                     data.frame(x=1:50, y=sort(rgamma(50, 2, 1/3)), group="Gamma(2,1/3)"))
boxplotdata <- ddply(boxplotdata, .(group), transform, ymax=max(y), ymin=min(y), med=median(y))

g6 <- ggplot() + 
  geom_linerange(data=boxplotdata, aes(x=factor(group), ymax=ymax, ymin=ymin, colour=factor(group))) +
  ggtitle("geom_linerange") + scale_colour_discrete("Distribution") + xlab("Distribution")
g6
gg2animint(list(g6=g6), out.dir="geoms/linerange")
```
[Animint plot](geoms/linerange/index.html)

### geom\_histogram
```{r histogram}
g7 <- ggplot() + 
  geom_histogram(data=subset(boxplotdata, group=="Gamma(2,1/3)"), aes(x=y, fill=..count..), binwidth=1) + 
  ggtitle("geom_histogram")
g7
gg2animint(list(g7=g7), out.dir="geoms/histogram")
```
[Animint plot](geoms/histogram/index.html)

### geom\_violin
```{r violin}
g8 <- ggplot() + 
  geom_violin(data=boxplotdata, aes(x=group, y=y, fill=group, group=group)) +
  ggtitle("geom_violin")+ scale_fill_discrete("Distribution") + xlab("Distribution")
g8
gg2animint(list(g8=g8), out.dir="geoms/violin")
```
[Animint plot](geoms/violin/index.html)


### geom\_step
```{r step}
g9 <- ggplot() + geom_step(data=boxplotdata, aes(x=x, y=y, colour=factor(group), group=group)) +
  scale_colour_discrete("Distribution") +
  ggtitle("geom_step")
g9
gg2animint(list(g9=g9), out.dir="geoms/step")
```
[Animint plot](geoms/step/index.html)


### geom\_contour
```{r contour}
library(reshape2) # for melt
contourdata <- melt(volcano)
names(contourdata) <- c("x", "y", "z")
g11 <- ggplot() + geom_contour(data=contourdata, aes(x=x, y=y, z=z), binwidth=4, size=0.5) + 
  geom_contour(data=contourdata, aes(x=x, y=y, z=z), binwidth=10, size=1) +
  ggtitle("geom_contour")
g11

gg2animint(list(g11=g11), out.dir="geoms/contour")
```
[Animint plot](geoms/contour/index.html)

```{r contourtile}
contourdata2 <- floor(contourdata/3)*3 # to make fewer tiles

g12 <- ggplot() + 
  geom_tile(data=contourdata2, aes(x=x, y=y, fill=z, colour=z)) + 
  geom_contour(data=contourdata, aes(x=x, y=y, z=z), colour="black", size=.5) +
  scale_fill_continuous("height", low="#56B1F7", high="#132B43", guide="legend") +
  scale_colour_continuous("height", low="#56B1F7", high="#132B43", guide="legend") +
  ggtitle("geom_tile + geom_contour") 
g12

gg2animint(list(g12=g12), out.dir="geoms/contour2")
```
[Animint plot](geoms/contour2/index.html). You may have to wait a moment to see the tiles - as each tile is a separate d3 object, it can take a few seconds to load all of the tiles. 

### scale\_y\_log10 and geom\_contour with stat\_density2d
While stat\_density2d does not always work reliably, we can still use the statistic within another geom, such as geom\_contour. 
```{r scaleycontour}
library("MASS")
data(geyser,package="MASS")
g13 <- ggplot() +  
  geom_point(data=geyser, aes(x = duration, y = waiting)) + 
  geom_contour(data=geyser, aes(x = duration, y = waiting), colour="blue", size=.5, stat="density2d") + 
  xlim(0.5, 6) + scale_y_log10(limits=c(40,110)) +
  ggtitle("geom_contour 2d density")
g13

gg2animint(list(g13=g13), out.dir="geoms/contour3")
```
[Animint plot](geoms/contour3/index.html)

### geom\_polygon with stat=density2d contours
```{r densitypolygon}
g14 <- ggplot() +  
  geom_polygon(data=geyser,aes(x=duration, y=waiting, fill=..level.., 
                               group=..piece..), 
               stat="density2d", alpha=.5) +
  geom_point(data=geyser, aes(x = duration, y = waiting)) + 
  scale_fill_continuous("Density Level", low="#56B1F7", high="#132B43") + 
  guides(colour = guide_legend(override.aes = list(alpha = 1)), 
         fill = guide_legend(override.aes = list(alpha = 1))) + 
  scale_y_continuous(limits=c(40,110), trans="log10") +
  scale_x_continuous(limits=c(.5, 6)) +
  ggtitle("geom_density2d polygon")
g14

gg2animint(list(g14=g14), out.dir="geoms/contour4")
```
[Animint plot](geoms/contour4/index.html)

### Tile plot filled by density 
```{r tiledensity}
data(diamonds)
dsmall <- diamonds[sample(nrow(diamonds), 1000), ] # reduce dataset size
g15 <- ggplot() + 
  geom_tile(data=dsmall, aes(x=carat, y=price, fill=..density.., colour=..density..), stat="density2d", contour=FALSE, n=30) +
  scale_fill_gradient(limits=c(1e-5,8e-4), na.value="white") + 
  scale_colour_gradient(limits=c(1e-5,8e-4), na.value="white") +
  ggtitle("geom_density2d tile") + ylim(c(0, 19000))
g15
gg2animint(list(g15=g15), out.dir="geoms/tiledensity")
```
[Animint plot](geoms/tiledensity/index.html)

### Density mapped to point size
```{r pointdensity}
g16 <- ggplot() + 
  geom_point(data=dsmall, aes(x=carat, y=price, alpha=..density..), 
             stat="density2d", contour=FALSE, n=10, size=I(1)) +
  scale_alpha_continuous("Density") +
  ggtitle("geom_density2d points")
g16
gg2animint(list(g16=g16), out.dir="geoms/pointdensity")
```
[Animint plot](geoms/pointdensity/index.html)

### Creating maps with animint
While geom\_map is not implemented in animint, it is possible to plot a map using geom\_polygon and merge. As map data frames can be rather large, it may be useful to use a point thinning algorithm, such as the **dp()** function in the **shapefiles** package [[link](http://cran.r-project.org/web/packages/shapefiles/shapefiles.pdf)] to reduce the number of points in each polygon. 

```{r maptutorial}
library(reshape2) # for melt
library(maps)

# obtain data for US Arrests
crimes <- data.frame(state = tolower(rownames(USArrests)), USArrests)
crimesm <- melt(crimes, id = 1)
# data frame should contain only counts of number of assaults
crimes.sub <- subset(crimesm, variable=="Assault") 

# load map for mainland US
states_map <- map_data("state")

# merge assault data with map data, so that each state 
# ("region" in the map dataframe) has a corresponding 
# entry for number of assaults.
assault.map <- merge(states_map, subset(crimesm, variable=="Assault"), by.x="region", by.y="state")
assault.map <- assault.map[order(assault.map$group, assault.map$order),]

g17 <- ggplot() + 
  geom_polygon(data=assault.map, aes(x=long, y=lat, group=group, fill=value, colour=value)) +
  expand_limits(x = states_map$long, y = states_map$lat) + 
  ggtitle("geom_polygon map") + ylim(c(12, 63)) + 
  geom_text(data=data.frame(x=-95.84, y=55, label="Arrests for Assault"), hjust=.5, aes(x=x, y=y, label=label))
g17  
gg2animint(list(g17=g17), out.dir="geoms/assaultmap")
```
[Animint plot](geoms/assaultmap/index.html)



### Stacked bar chart
While **geom\_bar** does not work well with clickSelects, it does work when creating a static plot. If you need to use clickSelects to select a specific bar, you should use **make\_bar**, **stat\_summary**, or calculate the relevant dataframe yourself using **ddply**. This ensures that clickSelects does not conflict with the specification of individual plot elements in **ggplot2**. See the [tornadoes tutorial](tornadoes.html#makebar) for more information and examples of clickSelects with **geom\_bar**. 
```{r stackedbar}
data(mtcars)
g18 <- ggplot() + geom_bar(data=mtcars, aes(x=factor(cyl), fill=factor(vs))) + ggtitle("geom_bar stacked")
g18

gg2animint(list(g18=g18), out.dir="geoms/stackedbar")
```
[Animint plot](geoms/stackedbar/index.html)



### **geom\_area** with **stat\_density**
```{r areadensity}
data(diamonds)
g19 <- ggplot() + 
  geom_area(data=diamonds, aes(x=clarity, y=..count.., group=cut, colour=cut, fill=cut), stat="density") +
  ggtitle("geom_area")
g19

gg2animint(list(g19=g19), out.dir="geoms/areaplot")
```
[Animint plot](geoms/areaplot/index.html)



### **geom\_freqpoly**
```{r freqpoly}
g20 <- ggplot() + 
  geom_freqpoly(data=diamonds, aes(x=clarity, group=cut, colour=cut)) +
  ggtitle("geom_freqpoly")
g20
gg2animint(list(g20=g20), out.dir="geoms/freqpoly")
```
[Animint plot](geoms/freqpoly/index.html)
